A Survey on Ordered Binary Decision Diagrams

### 2015-09-08 paper.tex
Fix paragraph content

\textit{Binary decision diagrams} (\textit{BDDs}) have been well studied since
Lee~\cite{LEE59} and especially Akers~\cite{AKERS78} introduced them. BDDs
represent a Boolean function $f$ as an acyclic, directed graph (DAG). Nodes
represent variables and have one incoming and two outgoing edges, each of which
denotes the variable evaluates to 0 (left) or 1 (right), respectively. There exist
two \textit{terminal} nodes, denoted \textbf{0} (\textbf{False}) and \textbf{1}
(\textbf{True}), which represent the result of $f$. To evaluate $f$ for a given
variable assignment, one just follows the path for the respective variable values
and the terminal node at the end is the result.
\tbr

>>>>

\textit{Binary decision diagrams} (\textit{BDDs}) have been well studied since
Lee~\cite{LEE59} and especially Akers~\cite{AKERS78} introduced them. BDDs
represent a Boolean function $f$ as an acyclic, directed graph (DAG). Nodes
represent variables and have one incoming and two outgoing edges, each of which
denotes the variable evaluates to 0 (left) or 1 (right), respectively. Whenever
the result of $f$ is fixed, an edge points to one of the constants 0 or 1.
To evaluate $f$ for a given variable assignment, one just follows the path for
the respective variable values. As soon as the path ends up in a constant, i.e. 
0 or 1, this constant value is the result of the variable assignment.
\tbr
